---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alaine Banninga"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 6
    highlight: pygments
    theme: spacelab
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows, 3 columns; dataset, x, y;

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

r = -0.0645

### Exercise 3

Extracting and plotting star data

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

finding the r-value for star data

```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

the r-value for the star data is -0.0630, which is a little weaker than the r-value for the dino data of -0.0645.

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```

the r-value for the circle data is -0.0683. this is a little big stronger than the r-value for the dino data of -0.0645.

### Exercise 5

Plotting all datasets at once, each in a different color and forming 3 columns of plots in the plot window and without a legend.

```{r}
ggplot(data = datasaurus_dozen, aes(x=x,y=y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) + 
  theme(legend.position = "none")
```

Finding the correlation coefficients for each dataset.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarise(r = cor(x,y)) %>%
  print(13)
```

